\LARGE \bf \acro: Reducing Supervisor Burden using SVM-based Risk to Efficiently Learn Robot Control Policies from Demonstrations {\color{blue}(v.10)}

### 2015-07-30 paper.tex
Version 10, ready for Anka's comments.

\title{\LARGE \bf \acro: Reducing Supervisor Burden using SVM-based Risk to Efficiently Learn Robot Control Policies from Demonstrations }

@@

\begin{abstract}
For robot control problems where no reward function is known and the dynamics of the environment are not specified, the
learning from demonstrations approach provides an algorithmic paradigm for learning a policy from supervisor-provided
demonstrations. Dataset Aggregation (DAgger) in particular yields a state of the art method in this context which treats
the problem of determining a policy as an iterative supervised learning problem which alternates between executing a
trained policy and acquiring new supervisor control inputs for roll-outs of a current best policy estimator. In this
work, we propose a novel algorithm, \acro~which is based on DAgger and which estimates the riskiness of states
encountered by the policy roll-outs by means of an approximate quantile super-levelset estimate of the distribution of
states used for training the current policy. Since learning a quantile function for high-dimensional input data is
challenging, we instead modify an SVN-based approach to quantile estimation that employs regularization to solve this
problem approximately. Our algorithm considers roll-outs with early termination as soon as a state outside a
user-defined quantile super-levelset is encountered. Our approach furthermore reduces the amount of neccessary
supervisor demonstrations by only collecting supervisor control inputs at states outside the current quantile estimate.
In experiments involving a simulated race track and in a Super Mario Atari game benchmark considered by the authors of
DAgger, our approach results in similar performance levels as DAgger while reducing the amount of required supervisor
control inputs by more than {\color{blue}[-- TODO --]} percent.
\end{abstract}

@@

\section{Introduction} 
Consider the problem of teaching a robot a complex task such cooking a meal or as racing a toy car around a track
against human opponents. When the robot is only provided with visual demonstrations without the knowledge or an
underlying cost function describing the task, traditional model based control approaches are often not applicable. In
these situations, the learning from demonstrations (LfD) approach provides a paradigmn for teaching the robot how to
accomplish the task \cite{ross2013learning,pomerleau1989alvinn,schulman2013case}.

One approach to LfD is to train a policy, or a function estimator (either a classifier or regressor), to predict a
supervisor's behavior given training data consisting of pairs of observations (input) and actions (output) performed
while accomplishing a task. Since the robot's actions typically affect the resulting next state, the resulting sequences
of states encountered during the execution of a policy are not independent random variables, thus making statistical
inference challenging. Ross et al. proved that this can cause the error in the policy estimator to compound over the
time and lead to performance degradation that is proportional to the time horizon of the task squared. The intuition
behind this result is that as the robot makes mistakes with respect to the supervisor's policy it drifts from the
distribution it was trained on and might encounter new states it can't generalize to.  Ross and Bagnell overcome this by
presenting an iterative method that first trains a policy on the data observed using standard supervised learning
techniques then tries (or 'rolls out') the policy out in the environment to see what states are likely to occur under
the robot's trained policy.  The supervisor then tells the robot what controls it should applied after each iteration
and the policy is retrained \cite{ross2010reduction}. The DAgger method has been successfully used since to teach a
robot how to follow verbal instructions, achieve state of the art performance on Atari games and fly a quad copter
through a forest~\cite{NIPS2014_5421,duvallet2013imitation,ross2013learning}.

\begin{figure}[t!]
\centering
\includegraphics[width=12cm, height=6cm]{figures/teaser.eps}
\caption{ 
Given a set of states corresponding to images of a race-track simulation (visualized in $\mathbb{R}^2$) with expert
control inputs, we consider a quantile super levelset estimate (shaded) as an approximation of the riskiness of
executing the trained policy at a given state. By varying the quantile threshold, we can increase or decrease the size
of the quantile super-levelset area. In our approach, points outside the super-levelset are considered risky and, during
training, roll-outs of the policy that leave the super-levelset require control demonstrations from the supervisor,
while roll-outs within the super-levelset can be performed autonomously.
}
\vspace*{-10pt}
\label{fig:dis_traveled}
\end{figure}

During learning, implementations of DAgger require the supervisor to manually provide control inputs that the robot
should have applied for each states it visits when rolling out the current best policy estimate. If the supervisor is a
human or an algorithm with a high time complexity, this can be tedious and expensive. We are hence interested in
reducing the burdon on the supervisor by partitioning the state space into states where the policy can either be
executed autonomously with little expected risk, or where supervisor control input (or 'labels') are likely to be
required due to high 'risk'. A state can be risky for 2 reasons: 1) we encounter a state which has a low density of
training data in its vicinity, which potentially means our policy will mis-predict the supervisor
\cite{tokdar2010importance} 2) the state is near previously visited states, but the control-input is mis-predicted
nonetheless. If an accurate density estimation corresponding to
the pairs of visited states and control signals is available, the first scenario can be captured by regions of
state-space with a low density estimate. Areas of low density are then considered to be risky since an insufficient data
is available to accurately model the demonstrator's policy. This idea is also captured in the notion that 'a trained
model will be able to generalize within the distribution it is trained on' \cite{tokdar2010importance} in statistical
machine learning. The second case arises for example when the current best policy estimate is locally inconsistent with expert
demonstrations.
%
%Vague!!!
%This property can be seen used in importance sampling when data is collected from one distribution, but tested on
%another and has to be re-weighted %to the test distribution \cite{huang2006correcting}. 
%
While the amount of data needed to accurately estimate the density increases exponentially with the dimension of state
space \cite{nadaraya1964estimating}, we can turn to approximate methods which instead attempt to learn an approximate
representation of the quantile levelsets of the distribution. Thus, we propose using a modified version the One Class
SVM method for support estimation that only tries to estimate the level set of the quantile function of the density
\cite{scholkopf2001estimating} at a user-determined quantile threshold which has been used even with high-dimensional
image data \cite{liu2014unsupervised}. Our modification furthermore removes areas of state space from the super-levelset
estimate where the local policy estimate is inconsistent with the expert demonstrations.

To apply our approach, we make the same assumptions as in the case of DAgger: 1) we require access to an environment
where a robot can try out (roll out) policies to sample trajectories and where we are able to collect observation states
and corresponding control inputs along these trajectories. 2) an interface allowing a supervisor to provide control
inputs that should have been applied for states along parts of the rolled out trajectories. 3) We assume that we are
able to collect a series of observations from the environment and the controls applied. 4) Lastly, for our theoretical
analysis to apply, we assume the current observation only depends on the previous observation and control input (i.e.
the Markovian assumption).

Our core contribution is the extension of DAgger to \acro~which incorporates a notion of risk to learning from
demonstrations and reduces supervisor
burdon by asking for supervisor demonstrations only in `risky' states. 
We achieve this by proposing a modified version of the One Class SVM, that both estimates the quantile level sets 
of the distribution of states with demonstrations and additionally
and carves out areas in the support where we know our policy will mis-predict the supervisor, thus identifying states of high
risk.  Our experimental results on a Super Mario Atari video game,  suggest \acro~is able to reach DAgger's
peak performance of surviving for an average of 2200 simulation steps with only 1200 queries to the supervisor, while DAgger required 2800 queries
averaged over 20 levels.
{\color{blue}[-- FINALIZE --]}

\section{Related Work}
The field of learning from demonstrations has achieved state of the art performance in a variety of areas within robotics
\cite{argall2009survey}. Abbeel et al.~used an iLQR controller based on helicopter trajectories demonstrated by a human expert
to successfully learn a series of aerobatics stunts \cite{abbeel2007application}. Billard and Matari used a hierarchy of
neural networks on video data and tracking markers to imitate the movement of human arms on a 37 degree of freedom humaniod
robot \cite{billard2001learning}. Schulman et al. used a non-linear warping technique based on thin-plate splines
to transer demonstrations of a human controlling a PR2 robot to tie knots with a rope to new and unseen initial
configurations of the~\cite{schulman2013case}.

A subset of research in the field of learning from demonstrations is working within the assumptions that the dynamics of
the robot and the environment are not known and that no access to a cost function describing a given task is available.
Under these assumptions, a set of trajectories and controls can be collected from a supervisor and the policy learning
problem can be treated as a supervised learning problem that determines a function from state space to
controls~\cite{argall2009survey} by means of regression. Pomerleau et al. used this approach on raw image data and
associated control inputs provided by a person driving a car. The authors then learned a policy that allowed a car to
travel on a highway. However, they observed that if the car deviated from the middle of the road the learned policy was
not able to recover, this behavior was attributed to the fact the car only drove in middle of the road while collecting
demonstrations~\cite{pomerleau1989alvinn}. Ross et al. studied this effect and showed that error can accumulate at a
rate quadratic in the time horizon of the policy in general. Ross et al. then proposed a learning algorithm, SMILE, that
stochastically mixes the supervisor's control with the robot's policy control signal during training, thus allowing the
robot to explore states the supervisor had not visited during training~\cite{ross2010efficient}.

Ross and Bagnell improved upon this method with DAgger (Dataset Aggregation) -- an iterative method that first trains a
policy on the data observed using standard supervised learning techniques and then tries, or 'rolls out' the policy in
the environment to see what states are likely to occur under the policy. The supervisor then tells the robot what
controls it should applied at each stage of this roll-out and the policy is retrained with an aggregate of all data seen
before \cite{ross2010reduction}. This algorithm has found widespread adoption in the robotics community. in
\cite{ross2013learning}, a quad-copter using DAgger learned how to fly through a forest using only Histogram of Gradient
(HOG) features extracted from camera images \cite{ross2013learning}. Guo et al. combined DAgger with Deep Q-learning
methods to achieve state of the art performance on a common Atari game benchmark in Reinforcement Learning
\cite{NIPS2014_5421}. Duvallet et al. furthermore used DAgger to teach robots to follow verbal instructions about where
to move sematically in a building with a training set consisting of of humans following similar verbal instructions
\cite{duvallet2013imitation}. Levine et al. very recently extended the iterative learning paradigm through Guided Policy
Search, which replaces the expert with iLQG and uses KL-divergence constraints to train the policy~\cite{levine2015end}.

One limitation of DAgger which we address in the present work is that it requires the demonstrator, or supervisor, to
provide control inputs that the expert would have applied for every state encountered along a roll-out of a trajectory at every interation of the
algorithm. Providing these control inputs can be very tedious or expensive both in the case where the `supervisor' is a
human or an algorithm with a high computational demand.

@@

%[Let's discuss this part]
{\color{blue}[-- IMPROVE THIS PARAGRAPH --]} In order to determine state space regions where a policy is likely to determine
an incorrect control input, we leverage a
property in statistical machine learning that a trained model will be able to generalize within the distribution it is
trained on \cite{tokdar2010importance}. This property is used in importance sampling when data is collected from one
distribution, but tested on another and has to be re-weighted to the test distribution \cite{huang2006correcting}. One
approach is to estimate the probability density of states the policy is trained on. However, the amount of data needed to accurately estimate the density scales exponentially in the number of \cite{nadaraya1964estimating}.

Several alternative approaches have been proposed to determine regions of state-space where an estimator is likely fail
to generalize away from the training-data \cite{markou2003novelty}. Knox and Ng \cite{knox1998algorithms} used a nearest
neighbor-based approach by estimating if a point was close to $k$ neighbors, however this approach was shown to be
susceptible to outliers since nearest neighbors mostly incorporate local information about the data. Manevitz and Yousef
\cite{manevitz2002one} trained a neural network filter to try and reconstruct the data and when the reconstruction error
at a point was high, the point was considered as likely to be outside of the estimators domain within which
generalization was possible. Manevitz and Yousef conjecture  that finding the right architecture can be task specific
and might require a large amount of hyperparameter tuning.

@@

\section{Problem Statement}
\subsection{Notation and Background}
{\color{blue} [-- TODO: SENSOR MODEL --]}
We denote by $\mathcal{X}$ the set consisting of \emph{observable states} for a robot task, consisting, for example of
high-dimensional vectors corresponding to images from a camera, or joint angles and object poses in the environment.
We furthermore consider a set $\mathcal{U}$ of \emph{allowable control inputs} for the robot, which can be discrete or continuous in
nature. The environment is
modeled to have dynamics that are stationary and Markovian, such that the the probability of state $\mathbf{x_{t+1}}\in
\mathcal{X}$ can be determined from the previous state $\mathbf{x}_t\in\mathcal{X}$ and control input $\mathbf{u}_t\in \mathcal{U}$,
so that $p(\bx_{N+1}|\bu_{N},\bx_{N}, \ldots, \bu_{0}, \bx_{0})=p(\bx_{N+1}|\bu_{N}, \bx_N)$.  
When no confusion arises, we denote the probability density over the initial state also by $p:\mathcal{X}\to
\mathbb{R}$. By a trajectory, we mean a finite series of pairs of $T$ states visited and corresponding
control inputs at these states $\tau = (\mathbf{x}_0,\mathbf{u}_1, ...., \mathbf{x}_T,\mathbf{u}_T)$, where $\bx_i\in \mathcal{X}$
and $\bu_i\in \mathcal{U}$ for $i\in \{0, \ldots, T\}$ and some $T\in \mathbb{N}$.  
At times we will also consider trajectories in state space only, in which case a trajectory corresponds
to a sequence of states $\tau = (\bx_0,....,\bx_T)$ with $\bx_i\in\mathcal{X}$ for $i\in \{0, \ldots, T\}$.

@@

$p(\bx_t|\theta)$ denote the value of the density of states visited at time $t$ if the robot follows the policy
$\pi_{\theta}$ for $t-1$ time steps which can be calculated by marginalization $p(\bx_t|\theta) =
\int_{\bx_{t-1}}...\int_{\bx_1} p((\bx_t,...,\bx_1)|\theta) d\bx_{t-1}...d\bx_1$. Following \cite{ross2010reduction},
the average density on states is now defined as $p(\bx|\theta) = \frac{1}{T} \sum^T_{t=1} p(\bx_t|\theta)$.
While we do not assume analytic knowledge of the distributions corresponding to: $p(\bx_{t+1}|\bx_t,\bu_t)$, $p(\bx_0)$, $p(\bx_{\bx}|
\bx)$ or $p(\bx|\theta)$, but instead assume that we have a stochastic real robot or a simulator such that for any state
$\bx_t$ and control $\bu_t$, we can sample the $\bx_{t+1}$ such that $\bx_{t+1}$ follows the distribution corresponding
to the density $p(\bx_{t+1}|\pi_{\theta}(\bx_t),\bx_t)$. In particular, when 'rolling out' trajectories under a policy
$\pi_{\theta}$, we utilize the robot or simulator to 'sample' the resulting stochastic trajectories rather than
estimating than estimating $p(\bx|\theta)$ itself.

Typically, the objective in policy learning can be framed as minimizing some cost function $C(\tau) = \sum^T_{t=1} c(\bx_t,\bu_t)$
of a trajectory $\tau = (\mathbf{x}_0,\mathbf{u}_1, ...., \mathbf{x}_T,\mathbf{u}_T)\in (\mathcal{X}\times
\mathcal{U})^{T+1}$. The cost function $c:\mathcal{X}\times \mathcal{U}\to \mathbb{R}$ is typically user defined and task specific. 
For example, in task of inserting a peg into a hole, the distance between the peg's current and desired final state can
be considered \cite{levine2015end}.  In our present setting, we do not know the cost function itself, but instead have access to a "supervisor", 
an algorithm or human that we assume uses some near-optimal policy $\tilde{\pi}$ to minimize $C(\tau)$, and we are given
an initial set of $N$ stochastic demonstration trajectories $\mathcal{D} = \lbrace \tilde{\tau}^1,...,\tilde{\tau}^N \rbrace$. 
which are the result of the supervisor applying this policy.

@@

Given a candidate policy $\pi_{\theta}$, we then use the surrogate loss function to approximately measure how "close" the policy's
returned control intput $\pi_{\theta}(\bx)\in \mathcal{U}$ at a given state $\bx\in \mathcal{X}$ is to the supervisor's policy's control output
$\tilde{\pi}(\bx)\in \mathcal{U}$. Our objective then consists of determining a policy $\pi_{\theta}$ minimizing the expected surrogate loss where the expectation is taken over the distribution of states.

@@

 \subsubsection{Step 2}
DAgger rolls out the policy $\pi_{\theta_{k=1}}$ to sample states that are likely to occur under $\theta_{k=1}$. For every state visited, DAgger requests the supervisor to provide the appropriate control/label. Formally, for a given sampled trajectory  $\tau = (\bx_0,\bu_0,...,\bx_T,\bu_T )$. The supervisor provides labels $\tilde{\bu}_t$, where $\bu_t \sim \pi(\bx_t) + \epsilon$ for $t\in \{0, \ldots, T\}$.
The states and labeled controls are then aggregated into the next data set of demonstrations $\mathcal{D}_1$.

Steps 1 and 2 are repeated for $K$ iterations or until the cumulative surrogate loss approaches zero. Since DAgger
requires rolling out the policy at each iteration, one way to terminate the algorithm is when the performance of the
rolled out policy matches the intended behavior, or more formally when the surrogate loss is below some predefined
threshold $\gamma$. {\color{blue} [-- F: Also talk about $\beta_i$ weights in DAgger --]}.

Dagger has been experimentally shown to perform  well in both simulation and real world experiments and furthermore
has guarantees guarantees the convergence to the supervisor's policy {\color{blue} [-- F: ONLY AN ERROR BOUND, RIGHT? --]}. 
However, policy rollouts can result in the robot entering dangerous states. For example, when DAgger was used on a
quad-copter the robot repeatedly crashed into trees before successfully learning to avoid them \cite{ross2013learning}.
We work under the assumption that a state can be risky for 2 reasons: 1) it lies in an area with a low density of
previously trained states, which potentially means our policy will mis-predict the supervisor and incur high surrogate
loss \cite{tokdar2010importance} 2) the surrogate loss of the current policy at the current state is high, so the state, although visited, does
not model the supervisor's control inputs correctly. Furthermore providing correct control inputs or ``labeling'' at each
iteration and each state in DAgger can be tedious or costly.

To address these limitations, we propose to 1) avoid highly risky states entirely by early termination the policy
roll-out that enter these regions and 2) to recognize non-risky states and to not request human input for these,
thereby reducing the burden on the human trainer.

>>>>

\title{\LARGE \bf \acro: Reducing Supervisor Burden using SVM-based Risk to Efficiently Learn Robot Control Policies
from Demonstrations {\color{blue}(v.10)} }

@@

\begin{abstract}
For robot control problems where no reward function is known and the dynamics of the environment are not specified, the
learning from demonstrations approach provides an algorithmic paradigm for learning a policy from supervisor-provided
demonstrations. Dataset Aggregation (DAgger) in particular yields a state of the art method in this context which treats
the problem of determining a policy as an iterative supervised learning problem. DAgger alternates between executing a
trained policy and acquiring new supervisor control inputs for roll-outs of a current best policy estimator. 
We propose a novel algorithm, \acro~ based on DAgger which estimates the riskiness of states
encountered by the policy roll-outs by means of an approximate quantile super-levelset estimate of the distribution of
states used for training the current policy and which additionally takes empirical surrogate loss of the current policy
into account. Since learning a quantile function for high-dimensional input data is
challenging, we instead modify an SVN-based approach to quantile estimation that employs regularization to solve this
problem approximately. Our algorithm considers roll-outs with early termination as soon as a state outside a
user-defined quantile super-levelset is encountered. Our approach empirically reduces the amount of neccessary
supervisor demonstrations by only collecting supervisor control inputs at states outside the current quantile estimate.
In experiments involving a simulated race track and in a Super Mario Atari game benchmark considered by the authors of
DAgger, our approach results in similar peak performance levels as DAgger while reducing the amount of required supervisor
control inputs by more than {\color{blue}[-- TODO --]} percent.
\end{abstract}

@@

\section{Introduction} 
Consider the problem of teaching a robot a complex task such cooking a meal or racing a toy car around a track
against human opponents. When the robot is only provided with visual demonstrations without the knowledge or an
underlying cost function describing the task, traditional model-based control approaches are often not applicable. In
these situations, the learning from demonstrations (LfD) approach provides a paradigmn for teaching the robot how to
accomplish the task \cite{ross2013learning,pomerleau1989alvinn,schulman2013case}.

One approach to LfD is to train a policy, or a function estimator (either a classifier or regressor), to predict a
supervisor's behavior given training data consisting of pairs of observations (input) and control inputs (output) performed
while accomplishing a task. Since the robot's actions typically affect the resulting next state, the resulting sequences
of states encountered during the execution of a policy are not independent random variables, thus making statistical
inference challenging. Ross et al. proved that this can cause the error in the policy estimator to compound over 
time and lead to performance degradation that is proportional to the time horizon of the task squared. The intuition
behind this result is that as the robot makes mistakes with respect to the supervisor's policy it drifts from the
distribution it was trained on and might encounter new states it can't generalize to.  Ross and Bagnell overcome this by
presenting an iterative method that first trains a policy on the data observed using standard supervised learning
techniques and then tries (or 'rolls out') the policy in the environment to see what states are likely to occur under
the robot's trained policy.  The supervisor then tells the robot what controls it should have applied after each iteration
and the policy is retrained \cite{ross2010reduction}. The DAgger method has been successfully used since to teach a
robot how to follow verbal instructions, achieve state of the art performance on Atari games and fly a quad copter
through a forest~\cite{NIPS2014_5421,duvallet2013imitation,ross2013learning}.

\begin{figure}[t!]
\centering
\includegraphics[width=12cm, height=6cm]{figures/teaser.eps}
\caption{ 
Given a set of states corresponding to images of a race-track simulation (visualized in $\mathbb{R}^2$) with expert
control inputs, we consider a modified quantile super-levelset estimate (shaded) as an approximation of the riskiness of
executing the trained policy at a given state. By varying the quantile threshold, we can increase or decrease the size
of the quantile super-levelset area. In our approach, points outside the super-levelset are considered risky and, during
training, roll-outs of the policy that leave the super-levelset require control input demonstrations from the supervisor,
while roll-outs within the super-levelset can be performed autonomously.
}
\vspace*{-10pt}
\label{fig:dis_traveled}
\end{figure}

During learning, implementations of DAgger require the supervisor to manually provide control inputs that the robot
should have applied for each states it visits when rolling out the current best policy estimate. If the supervisor is a
human or an algorithm with a high time complexity, this can be tedious or expensive. We are hence interested in
reducing the burdon on the supervisor by partitioning the state space into states where the policy can either be
executed autonomously with little expected risk, or where supervisor control input (or 'labels') are likely to be
required due to high risk. We postulate that a state can be risky for 2 reasons: 1) we encounter a state which has a low density of
training data in its vicinity, which potentially means our policy will mis-predict the supervisor
\cite{tokdar2010importance} 2) the state is potentially near previously visited states, but the control-input is mis-predicted
nonetheless. If an accurate density estimation corresponding to
the pairs of visited states and control signals is available, the first scenario can be captured by regions of
state-space with a low density estimate. Areas of low density are then considered to be risky since insufficient data
is available to accurately model the demonstrator's policy. This idea is also captured in the notion that 'a trained
model will be able to generalize within the distribution it is trained on' \cite{tokdar2010importance} in statistical
machine learning. The second case arises for example when the current best policy estimate is locally inconsistent with expert
demonstrations.
%
%Vague!!!
%This property can be seen used in importance sampling when data is collected from one distribution, but tested on
%another and has to be re-weighted %to the test distribution \cite{huang2006correcting}. 
%
While the amount of data needed to accurately estimate the density increases exponentially with the dimension of state
space \cite{nadaraya1964estimating}, we can turn to approximate methods which instead attempt to learn an approximate
representation of the quantile levelsets of the distribution. Thus, we propose using a modified version the One Class
SVM method for support estimation that only tries to estimate the level set of the quantile function of the density
\cite{scholkopf2001estimating} at a user-determined quantile threshold which has been used even with high-dimensional
image data \cite{liu2014unsupervised}. Our modification furthermore removes areas of state space from the super-levelset
estimate where the local policy estimate is inconsistent with the expert demonstrations in the sense that the incurred
surrogate loss of the current policy relative to the expert demonstration is above a threshold $\varepsilon>0$.

To apply our approach, we make the same basic assumptions as DAgger: 1) we require access to an environment
where a robot can try out (roll out) policies to sample trajectories and where we are able to collect observation states
and corresponding control inputs along these trajectories. 2) an interface allowing a supervisor to provide control
inputs that should have been applied for states along parts of the rolled out trajectories. 3) We assume that we are
able to collect a series of observations from the environment and the controls applied. 4) Lastly, for our theoretical
analysis to apply, we assume the current observation only depends on the previous observation and control input (i.e.
the Markovian assumption).

Our core contribution is the extension of DAgger to \acro~which incorporates a notion of risk to learning from
demonstrations and reduces supervisor burdon by asking for supervisor demonstrations only in `risky' states. We achieve
this by proposing a modified version of the One Class SVM, that both estimates the quantile level sets of the
distribution of states with demonstrations and additionally `carves out' areas in state space we know our policy
will mis-predict the supervisor, thus identifying states of high risk.  Our experimental results on a Super Mario Atari
video game, suggest \acro~is able to reach DAgger's peak performance of surviving for an average of 2200 simulation
steps with only 1200 queries to the supervisor, while DAgger required 2800 queries averaged over 20 levels.

\section{Related Work}
The field of learning from demonstrations has achieved state of the art performance in a variety of areas within robotics
\cite{argall2009survey}. Abbeel et al.~used an iLQR controller based on helicopter trajectories demonstrated by a human expert
to successfully learn a series of aerobatics stunts \cite{abbeel2007application}. Billard and Matari used a hierarchy of
neural networks on video data and tracking markers to imitate the movement of human arms on a 37 degree of freedom humaniod
robot \cite{billard2001learning}. Schulman et al. used a non-linear warping technique based on thin-plate splines
to transer demonstrations of a human controlling a PR2 robot to tie knots with a rope to new and unseen initial
configurations of the rope~\cite{schulman2013case}.

A subset of research in the field of learning from demonstrations is working with the assumptions that the dynamics of
the robot and the environment are not known and that no access to a cost function describing a given task is available.
Under these assumptions, a set of trajectories and controls can be collected from a supervisor and the policy learning
problem can be treated as a supervised learning problem that determines a function from state space to
controls~\cite{argall2009survey} by means of regression. Pomerleau et al. used this approach on raw image data and
associated control inputs provided by a person driving a car. The authors then learned a policy that allowed a car to
travel on a highway. However, they observed that if the car deviated from the middle of the road, the learned policy was
not able to recover. This behavior was attributed to the fact the car only drove in middle of the road while collecting
demonstrations~\cite{pomerleau1989alvinn}. Ross et al. studied this effect and showed that error can accumulate at a
rate quadratic in the time horizon of the policy in general. Ross et al. then proposed a learning algorithm, SMILE, that
stochastically mixes the supervisor's control with the robot's policy control signal during training, thus allowing the
robot to explore states the supervisor had not visited during training~\cite{ross2010efficient}.

Ross and Bagnell improved upon this method with DAgger (Dataset Aggregation) -- an iterative method that first trains a
policy on the data observed using standard supervised learning techniques and then tries, or 'rolls out' the policy in
the environment to see what states are likely to occur under the policy. The supervisor then tells the robot what
controls it should applied at each stage of this roll-out and the policy is retrained with an aggregate of all data seen
before \cite{ross2010reduction}. This algorithm has found widespread adoption in the robotics community. In
\cite{ross2013learning}, a quad-copter using DAgger learned how to fly through a forest using only Histogram of Gradient
(HOG) features extracted from camera images \cite{ross2013learning}. Guo et al. combined DAgger with Deep Q-learning
methods to achieve state of the art performance on a common Atari game benchmark in Reinforcement Learning
\cite{NIPS2014_5421}. Duvallet et al. furthermore used DAgger to teach robots to follow verbal instructions about where
to move sematically in a building with a training set consisting of of humans following similar verbal instructions
\cite{duvallet2013imitation}. In a related work, Levine et al. recently extended the iterative learning paradigm through Guided Policy
Search, which replaces the expert with iLQG and uses KL-divergence constraints to train the policy~\cite{levine2015end}.

One limitation of DAgger which we address in the present work is that it requires the demonstrator, or supervisor, to
provide control inputs that the expert would have applied for every state encountered along a roll-out of a trajectory
at every iteration of the algorithm. Providing these control inputs can be very tedious or expensive both in the case
where the `supervisor' is a human or an algorithm with a high computational cost.

@@

%[Let's discuss this part]
{\color{blue}[-- IMPROVE THIS PARAGRAPH --]} 
In order to determine state space regions where a policy is likely to determine an incorrect control input, we leverage
a common realization in statistical machine learning: a trained model will likely be able to generalize only in 
regions near which sufficient training data is available \cite{tokdar2010importance}. 
%F:Don't like this, discuss:
%This property is used in importance sampling when data is collected from one
%distribution, but tested on another and has to be re-weighted to the test distribution \cite{huang2006correcting}. 
One approach to estimate such regions is to estimate the probability density for the training data. However, the amount of data needed
to accurately estimate the density scales exponentially in the number of \cite{nadaraya1964estimating}.

Several alternative approaches have been proposed to determine regions of state-space where an estimator is likely fail
to generalize away from the training-data \cite{markou2003novelty}. Knox and Ng \cite{knox1998algorithms} used a nearest
neighbor-based approach by estimating if a point was close to $k$ neighbors, however this approach was shown to be
susceptible to outliers since nearest neighbors mostly incorporate local information about the data. Manevitz and Yousef
\cite{manevitz2002one} trained a neural network filter to try and reconstruct the data and when the reconstruction error
at a point was high, the point was considered as likely to be outside of the estimators domain within which
generalization was possible. Manevitz and Yousef conjecture that finding the right architecture for this purpose can be task specific
and might require a large amount of hyperparameter tuning.

@@

\section{Problem Statement}
\subsection{Notation and Background}
{\color{blue} [-- TODO: SENSOR MODEL --]}
We denote by $\mathcal{X}$ the set consisting of \emph{observable states} for a robot task. An example is given by
high-dimensional vectors corresponding to images from a camera, or the robot's joint angles and object poses in the environment.
We furthermore consider a set $\mathcal{U}$ of \emph{allowable control inputs} for the robot, which can be discrete or continuous in
nature. The environment is
modeled to have dynamics that are stationary and Markovian, such that the the probability of state $\mathbf{x_{t+1}}\in
\mathcal{X}$ can be determined from the previous state $\mathbf{x}_t\in\mathcal{X}$ and control input $\mathbf{u}_t\in \mathcal{U}$,
so that $p(\bx_{N+1}|\bu_{N},\bx_{N}, \ldots, \bu_{0}, \bx_{0})=p(\bx_{N+1}|\bu_{N}, \bx_N)$.  
When no confusion arises, we denote the probability density over the initial state also by $p:\mathcal{X}\to
\mathbb{R}$. By a trajectory, we mean a finite sequence of pairs of $T+1$ states visited and corresponding
control inputs at these states $\tau = (\mathbf{x}_0,\mathbf{u}_0, ...., \mathbf{x}_T,\mathbf{u}_T)$, where $\bx_i\in \mathcal{X}$
and $\bu_i\in \mathcal{U}$ for $i\in \{0, \ldots, T\}$ and some $T\in \mathbb{N}$.  
At times we will also consider trajectories in state space only, in which case a trajectory corresponds
to a sequence of states $\tau = (\bx_0,....,\bx_T)$ with $\bx_i\in\mathcal{X}$ for $i\in \{0, \ldots, T\}$.

@@

Let $p(\bx_t|\theta)$ denote the probability density value of a state visited at time $t$ if the robot follows the policy
$\pi_{\theta}$ for $t-1$ time steps which can be calculated by marginalization $p(\bx_t|\theta) =
\int_{\bx_{t-1}}...\int_{\bx_1} p((\bx_t,...,\bx_1)|\theta) d\bx_{t-1}...d\bx_1$. Following \cite{ross2010reduction},
the average density on states is now defined as $p(\bx|\theta) = \frac{1}{T} \sum^T_{t=1} p(\bx_t|\theta)$.
While we do not assume analytic knowledge of the distributions corresponding to: $p(\bx_{t+1}|\bx_t,\bu_t)$, $p(\bx_0)$, $p(\bx_{\bx}|
\bx)$ or $p(\bx|\theta)$, we instead assume that we have a stochastic real robot or a simulator such that for any state
$\bx_t$ and control $\bu_t$, we can sample the resulting next state $\bx_{t+1}$ from the distribution corresponding
to the density $p(\bx_{t+1}|\pi_{\theta}(\bx_t),\bx_t)$. In particular, when `rolling out' trajectories under a policy
$\pi_{\theta}$, we utilize the robot or simulator to `sample' the resulting stochastic trajectories rather than
estimating $p(\bx|\theta)$ itself.

Typically, the objective in policy learning can be framed as minimizing some cost function $C(\tau) = \sum^T_{t=1} c(\bx_t,\bu_t)$
of a trajectory $\tau = (\mathbf{x}_0,\mathbf{u}_1, ...., \mathbf{x}_T,\mathbf{u}_T)\in (\mathcal{X}\times
\mathcal{U})^{T+1}$. The cost function $c:\mathcal{X}\times \mathcal{U}\to \mathbb{R}$ is typically user defined and task specific. 
For example, for the task of inserting a peg into a hole, the distance between the peg's current and desired final state can
be considered \cite{levine2015end}.  In our present setting, we do not know the cost function itself, but instead have
access to a ``supervisor'', 
an algorithm or human that we assume uses some near-optimal policy $\tilde{\pi}$ to minimize $C(\tau)$, and we are given
an initial set of $N$ stochastic demonstration trajectories $\mathcal{D} = \lbrace \tilde{\tau}^1,...,\tilde{\tau}^N \rbrace$. 
which are the result of the supervisor applying this policy.

@@

Given a candidate policy $\pi_{\theta}$, we then use the surrogate loss function to approximately measure how close the policy's
returned control intput $\pi_{\theta}(\bx)\in \mathcal{U}$ at a given state $\bx\in \mathcal{X}$ is to the supervisor's policy's control output
$\tilde{\pi}(\bx)\in \mathcal{U}$. Our objective then consists of determining a policy $\pi_{\theta}$ minimizing the expected surrogate loss where the expectation is taken over the distribution of states.

@@

 \subsubsection{Step 2}
 DAgger rolls out the policy $\pi_{\theta_{k=1}}$ to sample states that are likely to occur under $\pi_{\theta_{k=1}}$.
 For every state visited, DAgger requests the supervisor to provide the appropriate control/label after the roll-out is
 finished. Formally, for a given sampled trajectory  $\tau = (\bx_0,\bu_0,...,\bx_T,\bu_T )$. The supervisor provides
 labels $\tilde{\bu}_t$, where $\bu_t \sim \tilde{\pi}(\bx_t) + \epsilon$ for $t\in \{0, \ldots, T\}$.
The states and labeled controls are then aggregated into the next data set of demonstrations $\mathcal{D}_1$.

Steps 1 and 2 are repeated for $K$ iterations or until the cumulative surrogate loss approaches zero or is below a
predefined threshold.

{\color{blue}[-- F: Also talk about $\beta_i$ weights in DAgger --]}.

Dagger has been experimentally shown to perform  well in both simulation and real world experiments and furthermore
has guarantees guarantees the convergence to the supervisor's policy {\color{blue} [-- F: ONLY AN ERROR BOUND, RIGHT? --]}. 
However, policy rollouts can result in the robot entering dangerous states. For example, when DAgger was used on a
quad-copter the robot repeatedly crashed into trees before successfully learning to avoid them \cite{ross2013learning}.
We work under the assumption that a state can be risky for 2 reasons: 1) it lies in an area with a low density of
previously trained states, which potentially means our policy will mis-predict the supervisor and incur high surrogate
loss \cite{tokdar2010importance} 2) the surrogate loss of the current policy at the current state is high, so that at
that state, supervisor's policy is not correctly approximated. Furthermore providing correct control inputs or ``labeling'' at each
iteration and each state in DAgger can be tedious and costly.

\emph{To address these limitations, we propose to 1) avoid highly risky states entirely by early termination the policy
roll-out that enter these regions and 2) to recognize non-risky states and to not request human input for these,
thereby reducing the burden on the human trainer. }

One way to define risk is to consider the distance between a state and a nearest neighbor in the training set, but this approach is vulnerable to
outliers. Another option is to fit a density to the training set, which requires an
exponential number of samples in the dimension of the state space \cite{nadaraya1964estimating}. We propose using a
modified version of the technique known as the One Class SVM that implicitly and approximately estimates a boundary of a user defined quantile of
a density representing the training data in $\mathcal{X}$ \cite{scholkopf2001estimating}.
